Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-26 WRITEUP/ms.tex
send this 1st draft to DR

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as bandpass calibrators for both tracks.
MWC349 and 3C279 were observed as the primary flux calibrator for C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

@@

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
were carried out under the D array configurations of the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
bandpass calibrators for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

@@

\subsection{VLA} %DONE
Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz). Since these data have not been
published, we here describe the details of the observations as well as our calibration steps.

@@

% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
The first and second moment maps are clipped at 3$\sigma$.
The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
map. The deconvolved source size is estimated to be 5\farcs1$\pm$0\farcs72 $\times$ 3\farcs72$\pm$0\farcs66
and thus the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as 2D-Gaussian,
the fit recovers the line intensity enclosed within the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein Ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a
kinematically-ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of its implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66\,$\pm$\,0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

@@

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux
$S_\nu$\,=\,800$\pm$88\,\micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

@@

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the background emission from the
observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry.
We then fit a power-law spectrum $S_\nu \propto \nu^\alpha$ to the
decomposed IRAC photometry to disentangle the observed total flux
at MIPS 24$\micron$. We find a spectral index of $\alpha\sim-$1.8 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean 3.6$-$8\,$\micron$
spectral slope of
$\alpha$\,=\,$-$1.07\,$\pm$\,0.53 found for unobscured AGN
\citep{Stern05a}. An extrapolation of the fit to 24$\micron$
yields 33.96\,$\pm$\,0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
for the foreground galaxy and RXJ1131, respectively.
We note that the IRAC photometry includes
emission from old stellar population and is prone to
dust extinction. Hence, the decomposed fluxes are only
our best estimate of the warm dust emission.
We incorporate the decomposed 24$\micron$ point in our
SED fitting to provide some constraints on
the Wien tail beyond the dust peak
of the spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the modes %in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence intervals in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

In the first model, we include the 24\,$\micron$ data
to constrain the power-law index. Based on the
best-fit of this model, we find a
\fir luminosity (rest-frame 42.5$-$122.5\,$\micron$) of
3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
dust mass of 22\petm{5}{18}\E{8}\,\Msun.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0\,$\micron$
(rest frame; \citealt{Dunne03a}).
The dust mass uncertainty does not
include those in the absorption coefficient.
These values are not corrected for lensing.

@@

To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200 in C13).
If we instead adopt the
more generally used definition for the total IR luminosity
(\LIR\,$>$\,10$^{12}$), RXJ1131 would be
considered a ULIRG given its lensing-corrected
total IR luminosity of $\sim$2\E{12}\,\Lsun.

@@

\subsubsection{SFE and Depletion Time}
We derive the SFE using the far-IR luminosity definition used by
C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
timescale of $\tau$\,=\,0.19\pmm0.07\,Gyr. % 5.8/SFE
This is substantially lower than most U/LIRGs (\citealt{Combes11a}; C13,
and references therein).
\textbf{ am I doing something wrong...}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a gas-rich companion, but how does
this affect its internal dynamics and what is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

While our result is consistent with other studies of RXJ1131, it
contrast strongly with studies of local (U)LIRGs/mergers
(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where active AGN are
typically found in late stage mergers
\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
that only major mergers near their final
coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
\citep[\eg][]{Carpineti15a,Larson16a}.
If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
is a major merger near its final coalescence and that the spatially offset
component is an expulsion of gas driven by AGN winds or is some
tidally ejected material from previous passage.
In that case, the molecular gas fraction in the host
galaxy should have declined (as in ellipticals) compared to early
stage mergers (can we find molecular gas mass fraction as a
function of merger stage?) and that the molecular gas would
be more concentrated in the nuclear region.
This is inconsistent with what
is observed (which strongly favors a disk morphology;
but there are outliers --  \citet{Ueda14a} find
extended molecular gas in merger remnant) and
the fact that there is on-going \SF activity.
Hence, we reject this and speculate the discrepancy is a consequence
of (the power source of) IR luminous galaxies are already very different by this redshift.

An alternative explanation might be that the
CO is less strongly-magnified as compared to the dust emission,
in which case, the lensing-corrected \LFIR is overestimated.
This is plausible given the extent of the source with respect to the caustics
and that substantial differential lensing effect has been seen across CO and other
wavelengths. If we instead use the NIR ($H$-band) magnification factor ($\mu_{\rm L}$\,=\,BLAH; C06),
we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
merger in the context of the results reported by \citet{Carpineti15a} and \citet{Larson16a}.

\subsubsection{Fate of RXJ1131-1231}
Has RXJ1131 encountered with the companion?

Mergers are observable for 0.2-0.4 Gyr,
between 2nd passage and coalescence.
Kinematic asymmetries follow morphological asymmetries during
mergers. Mergers are kinematically detectable for 0.2-0.4 Gyr
between second passage and coalescence.

Numerical simulations of mergers have shown that
multiple starburst episodes can be triggered even in double mergers.
The timing of the starbursts is thought to depend on the progenitor galaxy
morphologies, with early starbursts (before the galaxies start to merge)
occurring in bulges disc galaxies, and late starbursts (after the galaxies
have started to merge) occurring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
The spinning black hole already encountered?

The future of RXJ1131:
classical picture is that merger will evolve into local ellipticals, but more
recent studies (springel \& Hernquist 05, cite) suggest that mergers can also
form local large-disks (bulge dominated) $<--$ double check this. Given the
extended molecular gas distribution, we suggest RXJ1131 may evolve into the
latter (large-disk) unless the ``companion'' BKAH SOME STUFF or some other
mechanisms at play in the latter stage, transporting the gas
toward the central nuclear region.

\subsection{ULIRG Evolution and Cosmic SFH}
At low redshifts, the luminosity function of ULIRG shows strong evolution with
redshift (Veilleux et al. 1999). It is not known whether the IR luminosity of
these high-$z$ sources arises due to mergers between two or more large spiral
galaxies, as in local ULIRGs, or via a different mechanism/galaxy formation
processes at high-z.

% AGN contribution.

% Implication on SFH
Our result indicates that the gas mass fraction has already decreased
at this redshift, which may suggest that the change in cosmic SFD is due to
change in gas content. The SFE is also BLAH at this redshift,
consistent with current speculation of how the SFRD decreases over cosmic time.

@@

We observed the cold molecular gas properties using \bco and \cco line emission
toward the AGN host galaxy RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
Our results suggest that RXJ1131 is a wet-wet merger between a AGN/starburst
ULIRG and a optically faint companion.

Fitting SED models, we find that the AGN host galaxy is a ULIRG.
A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.

% any further work needed to resolve the remaining problems
We list several pieces of evidence through out
this work to argue that RXJ1131 is likely a rotating disk.
The double-horned profile, smooth, symmetric velocity field
seen in our lens model and in the
image plane and C06 model $n$=1 Sersic profile all suggest
a kinematically-order (i.e., disk) galaxy.
Yet, these are insufficient to conclude a disk morphology. Additional
characteristics such as peak velocity dispersion at the central region and a
``spider'' diagram are needed, which is commonly seen in local spirals.
The high dispersion near the dynamical center also
suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
data are needed to confirm this.

>>>>

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as the primary flux calibrator for C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

@@

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
were carried out under the D array configurations of the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

@@

\subsection{VLA} %DONE
Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz). Since the observations have not been described in any previous publications, 
we here describe their details as well as our calibration steps.

@@

% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
The first and second moment maps are clipped at 3$\sigma$.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
map. The deconvolved source size is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66
and thus the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as 2D-Gaussian,
the fit recovers the line intensity enclosed within the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein Ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a
kinematically-ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of its implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

@@

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux
$S_\nu$\,=\,800\pmm88\,\micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

@@

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the background emission from the
observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry.

We fit a power-law spectrum to the
decomposed IRAC photometry to disentangle the observed total flux
at MIPS 24$\micron$. We find a spectral index of $\alpha\sim-$1.8 and
$\alpha\sim-0.85$ for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean 3.6\,$-$\,8\,$\micron$
spectral slope of
$\alpha$\,=\,$-$1.07\,$\pm$\,0.53 found for unobscured AGN
\citep{Stern05a}. An extrapolation of the fit to 24$\micron$
yields 33.96\,$\pm$\,0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
for the foreground galaxy and RXJ1131, respectively.
We note that the IRAC photometry includes
emission from old stellar population and is prone to
dust extinction. Hence, the decomposed fluxes are only
our best estimate of the warm dust emission.
We incorporate the decomposed 24$\micron$ point in our
SED fitting to provide some constraints on
the Wien tail beyond the dust peak
of the spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000\,$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the modes %in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence intervals in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

In the first model, we include the 24\,$\micron$ data
to constrain the power-law index. Based on the
best-fit of this model, we find a
\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
dust mass of 22\petm{5}{18}\E{8}\,\Msun.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0\,$\micron$
(rest frame; \citealt{Dunne03a}).
The dust mass uncertainty does not
include those in the absorption coefficient.
These values are not corrected for lensing.

@@

To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40\,$-$\,500\,\micron)\footnote{We also note that the
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200 in C13).
If we instead adopt the
more generally used definition for the total IR luminosity
(\LIR\,$>$\,10$^{12}$), RXJ1131 would be
considered a ULIRG given its lensing-corrected
total IR luminosity of $\sim$2\E{12}\,\Lsun.

@@

\subsubsection{SFE and Depletion Time}
We derive the SFE using the far-IR luminosity definition used by
C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
timescale of $\tau$\,=\,190\pmm70\,Myr. % 5.8/SFE Gyr
This SFE is substantially lower than most U/LIRGs
(\citealt{Solomon97a,Combes11a}; C13). % local ULIRG: 180 +/- 160 Lsun/M (Solomon+97)
% Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.
\textbf{ am I doing something wrong...}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a
gas-rich companion, but how does this affect its internal dynamics?
What is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

While our result is consistent with other studies of RXJ1131, it
contrast strongly with studies of local (U)LIRGs/mergers
(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where AGNs are
typically found in late stage mergers
\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
that only these major mergers near their final
coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
\citep[\eg][hereafter L16]{Carpineti15a,Larson16a}
\footnote{In this section, we adopt the total IR luminosity
calculated from 8\,$-$\,1000\,\micron
to be consistent with the classification used by these authors.}.
If this is also the case at $z$$\sim$0.65, it would imply RXJ1131
is a major merger near its final coalescence and that the spatially offset
component is likely an expulsion of gas driven by AGN winds or some
tidally ejected material from previous passage.
In that case, the molecular gas fraction in the host
galaxy should have declined (as seen in ellipticals) compared to early
stage mergers
\textbf{can we find molecular gas mass fraction as a
function of merger stage? also, what is the dynamical mass for RXJ1131}
and that the molecular gas would
be more concentrated in the nuclear region.
This is inconsistent with what
is observed for RXJ1131
(an extended gas-rich disk; but see also U14 for outliers
with extended molecular gas in merger remnants) and
the fact that there is on-going \SF activity.
Hence, we reject this and speculate the discrepancy is a consequence
of different power mechanisms of IR-luminous galaxies at intermediate redshift.

An alternative explanation might be that the
CO is less strongly-magnified as compared to the dust emission,
in which case, the lensing-corrected IR luminosity is overestimated.
This is plausible given the extent of the source with respect to the caustics
and that substantial differential lensing effect has been seen across
CO and other wavelengths. If we instead use the NIR ($H$-band) magnification
factor ($\mu_{\rm L}$\,=\,BLAH; C06),
we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is
a large gas-rich LIRG, and a minor merger in the context of the results
reported by \citet{Carpineti15a} and L16.

{\bf --- anything below is not ready ---}
\subsubsection{Fate of RXJ1131-1231}
Has RXJ1131 encountered with the companion?

From numerical simulations, mergers are observable and distinguishable
with their kinematic and morphological features for 0.2$-$0.4 Gyr
between their second passage and final coalescence.

The spinning black hole in RXJ1131 provide one piece of
evidence that the two has already encountered.

% The future of RXJ1131:
Mergers are expected to evolve into
local ellipticals or large-disks (bulge dominated) (springel \& Hernquist 05, cite).
Given the
extended molecular gas distribution, we suggest RXJ1131 may evolve into the
latter (large-disk) unless the ``companion'' BKAH SOME STUFF or some other
mechanisms at play in the latter stage, transporting the gas
toward the central nuclear region and blah.

\subsection{ULIRG Evolution and Cosmic SFH}
While there is an emerging consensus on the strong
evolution of the IR luminosity function \citep[\eg][]{Huynh07a,Seymour10a},
it is currently unclear whether the IR luminosity of
these intermediate redshift sources arise due to the merging of large spiral
galaxies, as typically seen in local ULIRGs, or proceed under a different
formation processes at higher redshifts. Our study blah...

% Implication on SFH
Our result indicates that...
% the gas mass fraction has already decreased
% at this redshift, which may suggest that the change in cosmic SFD is due to
% change in gas content. The SFE is also BLAH at this redshift,
% consistent with current speculation of how the SFRD decreases over cosmic time.

@@

We investigate the cold gas kinematics and dynamics in
the lensed optical quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65
by observing its \bco and \cco line emission.
Our results suggest that RXJ1131 is a wet-wet merger between an AGN/starburst
ULIRG and a optically faint companion.

% Fitting SED models, we find that the AGN host galaxy is a ULIRG.
% A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.

% % any further work needed to resolve the remaining problems
% We list several pieces of evidence through out
% this work to argue that RXJ1131 is likely a rotating disk.
% The double-horned profile, smooth, symmetric velocity field
% seen in our lens model and in the
% image plane and C06 model $n$=1 Sersic profile all suggest
% a kinematically-order (i.e., disk) galaxy.
% Yet, these are insufficient to conclude a disk morphology. Additional
% characteristics such as peak velocity dispersion at the central region and a
% ``spider'' diagram are needed, which is commonly seen in local spirals.
% The high dispersion near the dynamical center also
% suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
% implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
% data are needed to confirm this.
